---
title: "Synthesis: model parameters, data table, and data summaries"
author: "K. Kraskura"
date: "`r Sys.Date()`"
output: html_document

---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

### Metabolic scaling with temperature and species ecologies 

```{r Prep runs, include = F}
date.imports<-substr(list.files("../Data_exports/Phylo/")[1], start = 17, stop = 26)
getModelCIs<-FALSE
source("phylo_mixed model.R")
```

### Mixed models (`evolvability::Almer`)

Rationale behind each model:

- model sets: Different random effects 
  + set 0: `(1|species)` = species intercept only
  + set 1: `(1|species) + (1|species:trial)` = species, and nested trial under species intercepts
  + set 2: `(1|species) +(0 + tempTestK1000|species) + (1|species:trial)` = species intercept, nested trial under species intercept, species-specific response to temperature (i.e. different size individuals of the same species, woutl have differe sensititivy to temperature). 
  + set 3: _(models lead to singular fits, these were no longer considered)_
  + set 4: `(1|species) +(0 + lnBWg|species) + (1|species:trial)` = species intercept, nested trial under species intercept, species-specific mass scaling slopes 
  + set 5: `(1|species) +(0 + lnBWg|species:trial) + (1|species:trial)` = species intercept, nested trial under species intercept, nested species:trial mass scaling slopes
- model types: 
  + mass and temperature affect metabolism independently 
  + (`int`) mass and temperature affect metabolism in interaction 
  + (`.POLY`) nonlinear polynomial Arrhenius temperature response 
  + (`intPOLY`) nonlinear polynomial Arrhenius temperature response that changes with body mass (interaction nonlinear temp X mass)

- Not printed below, but constructed were also models for MMR, AAS, and FAS. BIC comparison for these is shown below.  Specifically compared were: 
  1. best non-phylogeny model (thesis)
  2. equivalent phylogeny model


### 1. BIC RMR - optimal temperatures
```{r, echo = FALSE, fig.align = 'left'}
RMR_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)
    
# Phylo model can be used in model selection 
```
<br>

### 2. BIC RMR - warm temperatures

```{r, echo = FALSE}
RMR_W_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)

# knitr:::kable(RMR_W_BIC%>%   kbl(digits = 2) %>%   kable_classic_2(full_width = F)      # Phylo model can be used in model selection 
```

<br>

### 3. BIC MMR - optimal temperatures

```{r, echo = FALSE}
MMR_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)
```

<br>

### 4. BIC MMR - warm temperatures
```{r, echo = FALSE}
MMR_W_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)
    # Phylo model can be used in model selection 
```

<br>

### 5. BIC Absolute AS - optimal temperatures
```{r, echo = FALSE}
AS_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)
    # Phylo model can be used in model selection 
```

<br>

### 6. BIC Absolute AS - warm temperatures
```{r, echo = FALSE}
AS_W_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)
    # Phylo model can be used in model selection 
```

<br>

### 7. BIC Factorial AS - optimal temperatures
```{r, echo = FALSE}
FAS_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)
    # Phylo model can be used in model selection 
```

<br>

### 8. BIC Factorial AS - warm temperatures
```{r, echo = FALSE}
FAS_W_BIC %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)
    # Phylo model can be used in model selection 
```

## Best models summries:

### Ecologically relevant 
```{r model summaries, echo =F }
# Ecol relev
summary(rmr_mod_ER)
summary(amr_mod_ER)
summary(fas_mod_ER)
summary(as_mod_ER)
```


### Warm fish
```{r model summaries warm, echo = F}
# warm
summary(rmr_mod_W)
summary(amr_mod_W)
summary(fas_mod_W)
summary(as_mod_W)
```

 
## Summary data 
```{r min max data, echo = F}
sum_data %>%
  kbl(digits = 2) %>%
  kable_classic_2(full_width = F)

```

## Scaling parameters 

```{r scaling parameters, echo = F}
scaling.params %>%
  mutate_at(c('lnBWg', "(Intercept)", 'tempTestK1000', "E(ev)"), as.numeric) %>% 
  kbl(digits = 3) %>%
  kable_classic_2(full_width = F)

```


## Confidence intervals 

```{r}

sum_CItable %>% 
  kbl(digits = 3) %>%
  kable_classic_2(full_width = F)

```

